\poemchapter{The Wood-Cutter}

\begin{poemblock}
\indentedblock\itshape{
The sky is like an envelope,\\
\idt One of those blue official things;\\
And, sealing it, to mock our hope,\\
\idt The moon, a silver wafer, clings.\\
What shall we find when death gives leave\\
To read--our sentence or reprieve?
}

I'm holding it down on God's scrap-pile, up on the fag-end of earth;\\
\idt O'er me a menace of mountains, a river that grits at my feet;\\
Face to face with my soul-self, weighing my life at its worth;\\
\idt Wondering what I was made for, here in my last retreat.

Last!  Ah, yes, it's the finish.  Have ever you heard a man cry?\\
\idt (Sobs that rake him and rend him, right from the base of the chest.)\\
That's how I've cried, oh, so often; and now that my tears are dry,\\
\idt I sit in the desolate quiet and wait for the infinite Rest.

Rest!  Well, it's restful around me; it's quiet clean to the core.\\
\idt The mountains pose in their ermine, in golden the hills are clad;\\
The big, blue, silt-freighted Yukon seethes by my cabin door,\\
\idt And I think it's only the river that keeps me from going mad.

By day it's a ruthless monster, a callous, insatiate thing,\\
\idt With oily bubble and eddy, with sudden swirling of breast;\\
By night it's a writhing Titan, sullenly murmuring,\\
\idt Ever and ever goaded, and ever crying for rest.

It cries for its human tribute, but me it will never drown.\\
\idt I've learned the lore of my river; my river obeys me well.\\
I hew and I launch my cordwood, and raft it to Dawson town,\\
\idt Where wood means wine and women, and, incidentally, hell.

Hell and the anguish thereafter.  Here as I sit alone\\
\idt I'd give the life I have left me to lighten some load of care:\\
(The bitterest part of the bitter is being denied to atone;\\
\idt Lips that have mocked at Heaven lend themselves ill to prayer.)

\indentedblock\itshape{
Impotent as a beetle pierced on the needle of Fate;\\
\idt A wretch in a cosmic death-cell, peaks for my prison bars;\\
'Whelmed by a world stupendous, lonely and listless I wait,\\
\idt Drowned in a sea of silence, strewn with confetti of stars.
}

See! from far up the valley a rapier pierces the night,\\
\idt The white search-ray of a steamer.  Swiftly, serenely it nears;\\
A proud, white, alien presence, a glittering galley of light,\\
\idt Confident-poised, triumphant, freighted with hopes and fears.

I look as one looks on a vision; I see it pulsating by;\\
\idt I glimpse joy-radiant faces; I hear the thresh of the wheel.\\
Hoof-like my heart beats a moment; then silence swoops from the sky.\\
\idt Darkness is piled upon darkness.  God only knows how I feel.

Maybe you've seen me sometimes; maybe you've pitied me then--\\
\idt The lonely waif of the wood-camp, here by my cabin door.\\
Some day you'll look and see not; futile and outcast of men,\\
\idt I shall be far from your pity, resting forevermore.

\indentedblock\itshape{
My life was a problem in ciphers, a weary and profitless sum.\\
\idt Slipshod and stupid I worked it, dazed by negation and doubt.\\
Ciphers the total confronts me.  Oh, Death, with thy moistened thumb,\\
\idt Stoop like a petulant schoolboy, wipe me forever out!
}
\end{poemblock}
