\poemchapter{The Telegraph Operator}

\begin{poemblock}
I will not wash my face;\\
\idt I will not brush my hair;\\
I "pig" around the place--\\
\idt There's nobody to care.\\
Nothing but rock and tree;\\
\idt Nothing but wood and stone,\\
Oh, God, it's hell to be\\
\idt Alone, alone, alone!

Snow-peaks and deep-gashed draws\\
\idt Corral me in a ring.\\
I feel as if I was\\
\idt The only living thing\\
On all this blighted earth;\\
\idt And so I frowst and shrink,\\
And crouching by my hearth\\
\idt I hear the thoughts I think.

I think of all I miss--\\
\idt The boys I used to know;\\
The girls I used to kiss;\\
\idt The coin I used to blow:\\
The bars I used to haunt;\\
\idt The racket and the row;\\
The beers I didn't want\\
\idt (I wish I had 'em now).

Day after day the same,\\
\idt Only a little worse;\\
No one to grouch or blame--\\
\idt Oh, for a loving curse!\\
Oh, in the night I fear,\\
\idt Haunted by nameless things,\\
Just for a voice to cheer,\\
\idt Just for a hand that clings!

Faintly as from a star\\
\idt Voices come o'er the line;\\
Voices of ghosts afar,\\
\idt Not in this world of mine;\\
Lives in whose loom I grope;\\
\idt Words in whose weft I hear\\
Eager the thrill of hope,\\
\idt Awful the chill of fear.

I'm thinking out aloud;\\
\idt I reckon that is bad;\\
(The snow is like a shroud)--\\
\idt Maybe I'm going mad.\\
Say! wouldn't that be tough?\\
\idt This awful hush that hugs\\
And chokes one is enough\\
\idt To make a man go "bugs".

There's not a thing to do;\\
\idt I cannot sleep at night;\\
No wonder I'm so blue;\\
\idt Oh, for a friendly fight!\\
The din and rush of strife;\\
\idt A music-hall aglow;\\
A crowd, a city, life--\\
\idt Dear God, I miss it so!

Here, you have moped enough!\\
\idt Brace up and play the game!\\
But say, it's awful tough--\\
\idt Day after day the same\\
(I've said that twice, I bet).\\
\idt Well, there's not much to say.\\
I wish I had a pet,\\
\idt Or something I could play.

Cheer up! don't get so glum\\
\idt And sick of everything;\\
The worst is yet to come;\\
\idt God help you till the Spring.\\
God shield you from the Fear;\\
\idt Teach you to laugh, not moan.\\
Ha! ha! it sounds so queer--\\
\idt Alone, alone, alone!

\end{poemblock}
