\poemchapter{“FIGHTING MAC”}
\begin{poemblock}
 
A LIFE TRAGEDY

A pistol-shot rings round and round the world:\\
\hspace*{3em}In pitiful defeat a warrior lies.\\
A last defiance to dark Death is hurled,\\
\hspace*{3em}A last wild challenge shocks the sunlit skies.\\
\hspace*{3em}Alone he falls with wide, wan, woeful eyes:\\
Eyes that could smile at death—could not face shame.

Alone, alone he paced his narrow room,\\
\hspace*{3em}In the bright sunshine of that Paris day;\\
Saw in his thought the awful hand of doom;\\
\hspace*{3em}Saw in his dream his glory pass away;\\
\hspace*{3em}Tried in his heart, his weary heart, to pray:\\
"O God! who made me, give me strength to face\\
The spectre of this bitter, black disgrace."

The burn brawls darkly down the shaggy glen,\\
\hspace*{3em}The bee-kissed heather blooms around the door;\\
He sees himself a barefoot boy again,\\
\hspace*{3em}Bending o'er page of legendary lore.\\
\hspace*{3em}He hears the pibroch, grips the red claymore,\\
Runs with the Fiery Cross a clansman true,\\
Sworn kinsman of Rob Roy and Roderick Dhu.

Eating his heart out with a wild desire,\\
\hspace*{3em}One day, behind his counter trim and neat,\\
He hears a sound that sets his brain afire—\\
\hspace*{3em}The Highlanders are marching down the street.\\
\hspace*{3em}Oh, how the pipes shrill out, the mad drums beat!\\
"On to the gates of Hell, my Gordons gay!"\\
He flings his hated yardstick far away.

He sees the sullen pass, high-crowned with snow,\\
\hspace*{3em}Where Afghans cower with eyes of gleaming hate.\\
He hurls himself against the hidden foe.\\
\hspace*{3em}They try to rally—ah, too late, too late!\\
\hspace*{3em}Again, defenceless, with fierce eyes that wait\\
For death, he stands, like baited bull at bay,\\
And flouts the Boers, that mad Majuba day.

He sees again the murderous Soudan,\\
\hspace*{3em}Blood-slaked and rapine swept. He seems to stand\\
Upon the gory plain of Omdurman.\\
\hspace*{3em}Then Magersfontein, and supreme command\\
\hspace*{3em}Over his Highlanders. To shake his hand\\
A King is proud, and princes call him friend,\\
And glory crowns his life—and now the end.

The awful end. His eyes are dark with doom;\\
\hspace*{3em}He hears the shrapnel shrieking overhead:\\
He sees the ravaged ranks, the flame-stabbed gloom.\\
\hspace*{3em}Oh, to have fallen! the battle-field his bed,\\
\hspace*{3em}With Wauchope and his glorious brother-dead.\\
Why was he saved for this, for this? And now\\
He raises the revolver to his brow.

In many a Highland home, framed with rude art,\\
\hspace*{3em}You'll find his portrait, rough-hewn, stern and square:\\
It's graven in the Fuyam fellah's heart;\\
\hspace*{3em}The Ghurka reads it at his evening prayer;\\
\hspace*{3em}The raw lands know it, where the fierce suns glare;\\
The Dervish fears it. Honour to his name,\\
Who holds aloft the shield of England's fame.

Mourn for our hero, men of Northern race!\\
\hspace*{3em}We do not know his sin; we only know\\
His sword was keen. He laughed death in the face,\\
\hspace*{3em}And struck, for Empire's sake, a giant blow.\\
\hspace*{3em}His arm was strong. Ah! well they learnt, the foe.\\
The echo of his deeds is ringing yet,\\
Will ring for aye. All else ... let us forget.

\end{poemblock}
