\poemchapter{Grin}


\begin{poemblock}
If you're up against a bruiser and you're getting knocked about---\\
\hspace*{18em}\textbf{Grin.}\\
If you're feeling pretty groggy, and you're licked beyond a doubt---\\
\hspace*{18em}\textbf{Grin.}\\
Don't let him see you're funking, let him know with every clout,\\
Though your face is battered to a pulp, your blooming heart is stout;\\
Just stand upon your pins until the beggar knocks you out---\\
\hspace*{18em}\textbf{And grin.}


This life's a bally battle, and the same advice holds true,\\
\hspace*{18em}\textbf{Of grin.}\\
If you're up against it badly, then it's only one on you,\\
\hspace*{18em}\textbf{So grin.}\\
If the future's black as thunder, don't let people see you're blue;\\
Just cultivate a cast-iron smile of joy the whole day through;\\
If they call you ``Little Sunshine,'' wish that \textit{they'd} no troubles, too---\\
\hspace*{18em}\textbf{You may---grin.}


Rise up in the morning with the will that, smooth or rough,\\
\hspace*{18em}\textbf{You'll grin.}\\
Sink to sleep at midnight, and although you're feeling tough,\\
\hspace*{18em}\textbf{Yet grin.}\\
There's nothing gained by whining, and you're not that kind of stuff;\\
You're a fighter from away back, and you \textit{won't} take a rebuff;\\
Your trouble is that you don't know when you have had enough---\\
\hspace*{18em}\textbf{Don't give in.}\\
If Fate should down you, just get up and take another cuff;\\
You may bank on it that there is no philosophy like bluff\\
\hspace*{18em}\textbf{And grin.}
\end{poemblock}