\poemchapter{The Spell of the Yukon}

\begin{poemblock}
I wanted the gold, and I sought it;\\
\idt I scrabbled and mucked like a slave.\\
Was it famine or scurvy—I fought it,\\
\idt I hurled my youth into the grave.\\
I wanted the gold and I got it—\\
\idt Came out with a fortune last fall,—\\
Yet somehow life's not what I thought it,\\
\idt And somehow the gold isn't all.

No! There's the land. (Have you seen it?)\\
\idt It's the cussedest land that I know,\\
From the big, dizzy mountains that screen it,\\
\idt To the deep, deathlike valleys below.\\
Some say God was tired when He made it;\\
\idt Some say it's a fine land to shun;\\
Maybe: but there's some as would trade it\\
\idt For no land on earth—and I'm one.

You come to get rich (damned good reason),\\
\idt You feel like an exile at first;\\
You hate it like hell for a season,\\
\idt And then you are worse than the worst.\\
It grips you like some kinds of sinning;\\
\idt It twists you from foe to a friend;\\
It seems it's been since the beginning;\\
\idt It seems it will be to the end.

I've stood in some mighty-mouthed hollow\\
\idt That's plumb-full of hush to the brim;\\
I've watched the big, husky sun wallow\\
\idt In crimson and gold, and grow dim,\\
Till the moon set the pearly peaks gleaming,\\
\idt And the stars tumbled out, neck and crop;\\
And I've thought that I surely was dreaming,\\
\idt With the peace o' the world piled on top.

The summer—no sweeter was ever;\\
\idt The sunshiny woods all athrill;\\
The grayling aleap in the river,\\
\idt The bighorn asleep on the hill.\\
The strong life that never knows harness;\\
\idt The wilds where the caribou call;\\
The freshness, the freedom, the farness—\\
\idt O God! how I'm stuck on it all.

The winter! the brightness that blinds you,\\
\idt The white land locked tight as a drum,\\
The cold fear that follows and finds you,\\
\idt The silence that bludgeons you dumb.\\
The snows that are older than history,\\
\idt The woods where the weird shadows slant;\\
The stillness, the moonlight, the mystery,\\
\idt I've bade 'em good-bye—but I can't.

There's a land where the mountains are nameless,\\
\idt And the rivers all run God knows where;\\
There are lives that are erring and aimless,\\
\idt And deaths that just hang by a hair;\\
There are hardships that nobody reckons;\\
\idt There are valleys unpeopled and still;\\
There's a land—oh, it beckons and beckons,\\
\idt And I want to go back—and I will.

They're making my money diminish;\\
\idt I'm sick of the taste of champagne.\\
Thank God! when I'm skinned to a finish\\
\idt I'll pike to the Yukon again.\\
I'll fight—and you bet it's no sham-fight;\\
\idt It's hell!—but I've been there before;\\
And it's better than this by a damsite—\\
\idt So me for the Yukon once more.

There's gold, and it's haunting and haunting;\\
\idt It's luring me on as of old;\\
Yet it isn't the gold that I'm wanting,\\
\idt So much as just finding the gold.\\
It's the great, big, broad land 'way up yonder,\\
\idt It's the forests where silence has lease;\\
It's the beauty that thrills me with wonder,\\
\idt It's the stillness that fills me with peace.

\end{poemblock}
