\poemchapter{The Rhyme of the Restless Ones}


\begin{verse}
We couldn't sit and study for the law;\\
\hspace*{3em}The stagnation of a bank we couldn't stand;\\
For our riot blood was surging, and we didn't need much urging\\
To excitements and excesses that are banned.\\
So we took to wine and drink and other things,\\
\hspace*{3em}And the devil in us struggled to be free;\\
Till our friends rose up in wrath, and they pointed out the path,\\
And they paid our debts and packed us o'er the sea.

Oh, they shook us off and shipped us o'er the foam,\\
To the larger lands that lure a man to roam;\\
\hspace*{3em}And we took the chance they gave\\
\hspace*{3em}Of a far and foreign grave,\\
And we bade goodbye for evermore to home.

And some of us are climbing on the peak,\\
\hspace*{3em}And some of us are camping on the plain;\\
By pine and palm you'll find us, with never claim to bind us,\\
By track and trail you'll meet us once again.

We are fated serfs to freedom—sky and sea;\\
\hspace*{3em}We have failed where slummy cities overflow;\\
But the stranger ways of earth know our pride and know our worth,\\
And we go into the dark as fighters go.

Yes, we go into the night as brave men go,\\
Though our faces they be often streaked with woe;\\
\hspace*{3em}Yet we're hard as cats to kill,\\
\hspace*{3em}And our hearts are reckless still,\\
And we've danced with death a dozen times or so.

And you'll find us in Alaska after gold,\\
\hspace*{3em}And you'll find us herding cattle in the South.\\
We like strong drink and fun; and when the race is run,\\
\hspace*{3em}We often die with curses in our mouth.

We are wild as colts unbroke, but never mean;\\
\hspace*{3em}Of our sins we've shoulders broad to bear the blame;\\
But we'll never stay in town, and we'll never settle down,\\
\hspace*{3em}And we'll never have an object or an aim.

No, there's that in us that time can never tame;\\
And life will always seem a careless game;\\
\hspace*{3em}And they'd better far forget—\\
\hspace*{3em}Those who say they love us yet—\\
Forget, blot out with bitterness our name.

\end{verse}
