\poemchapter{The Call of the Wild}

\begin{poemblock}
Have you gazed on naked grandeur where there's nothing else to gaze on,\\
\idt Set pieces and drop-curtain scenes galore,\\
Big mountains heaved to heaven, which the blinding sunsets blazon,\\
\idt Black canyons where the rapids rip and roar?\\
Have you swept the visioned valley with the green stream streaking through it,\\
\idt Searched the Vastness for a something you have lost?\\
Have you strung your soul to silence? Then for God's sake go and do it;\\
\idt Hear the challenge, learn the lesson, pay the cost.

Have you wandered in the wilderness, the sage-brush desolation,\\
\idt The bunch-grass levels where the cattle graze?\\
Have you whistled bits of rag-time at the end of all creation,\\
\idt And learned to know the desert's little ways?\\
Have you camped upon the foothills, have you galloped o'er the ranges,\\
\idt Have you roamed the arid sun-lands through and through?\\
Have you chummed up with the mesa? Do you know its moods and changes?\\
\idt Then listen to the wild—it's calling you.

Have you known the Great White Silence, not a snow-gemmed twig a-quiver?\\
\idt (Eternal truths that shame our soothing lies.)\\
Have you broken trail on snowshoes? mushed your huskies up the river,\\
\idt Dared the unknown, led the way, and clutched the prize?\\
Have you marked the map's void spaces, mingled with the mongrel races,\\
\idt Felt the savage strength of brute in every thew?\\
And though grim as hell the worst is, can you round it off with curses?\\
\idt Then hearken to the wild—it's wanting you.

Have you suffered, starved, and triumphed grovelled, down, yet grasped at glory,\\
\idt Grown bigger in the bigness of the whole?\\
"Done things" just for the doing, letting babblers tell the story,\\
\idt Seeing through the nice veneer the naked soul?\\
Have you seen God in His splendours, heard the text that nature renders?\\
\idt (You'll never hear it in the family pew.)\\
The simple things, the true things, the silent men who do things—\\
\idt Then listen to the wild—it's calling you.

They have cradled you in custom, they have primed you with their preaching,\\
\idt They have soaked you in convention through and through;\\
They have put you in a showcase; you're a credit to their teaching—\\
\idt But can't you hear the wild?—it's calling you.\\
Let us probe the silent places, let us seek what luck betide us;\\
\idt Let us journey to a lonely land I know.\\
There's a whisper on the night-wind, there's a star agleam to guide us,\\
\idt And the wild is calling, calling ... let us go.

\end{poemblock}
