\poemchapter{The Pines}

\begin{poemblock}
We sleep in the sleep of ages, the bleak,\\
\idt barbarian pines;\\
The grey moss drapes us like sages, and closer\\
\idt we lock our lines,\\
And deeper we clutch through the gelid gloom\\
\idt where never a sunbeam shines.

On the flanks of the storm-gored ridges are our\\
\idt black battalions massed;\\
We surge in a host to the sullen coast, and we\\
\idt sing in the ocean blast;\\
From empire of sea to empire of snow we grip\\
\idt our empire fast.

To the niggard lands were we driven; 'twixt\\
\idt desert and foe are we penned.\\
To us was the Northland given, ours to stronghold\\
\idt and defend;\\
Ours till the world be riven in the crash of the\\
\idt utter end.

Ours from the bleak beginning, through the æons\\
\idt of death-like sleep;\\
Ours from the shock when the naked rock was\\
\idt hurled from the hissing deep;\\
Ours through the twilight ages of weary\\
\idt glacier-creep.

Wind of the East, wind of the West, wandering\\
\idt to and fro,\\
Chant your songs in our topmost boughs, that\\
\idt the sons of men may know\\
The peerless pine was the first to come, and the\\
\idt pine will be last to go!

We pillar the halls of perfumed gloom; we plume\\
\idt where the eagles soar;\\
The North-wind swoops from the brooding Pole,\\
\idt and our ancients crash and roar;\\
But where one falls from the crumbling walls\\
\idt shoots up a hardy score.

We spring from the gloom of the canyon's womb;\\
\idt in the valley's lap we lie;\\
From the white foam-fringe where the breakers\\
\idt cringe to the peaks that tusk the sky\\
We climb, and we peer in the crag-locked mere\\
\idt that gleams like a golden eye,—

Gain to the verge of the hog-back ridge where the\\
\idt vision ranges free:\\
Pines and pines and the shadow of pines as far as\\
\idt the eye can see;\\
A steadfast legion of stalwart knights in\\
\idt dominant empery.

Sun, moon and stars, give answer; shall we not\\
\idt staunchly stand\\
Even as now, forever, wards of the wilder strand,\\
Sentinels of the stillness, lords of the last lone land!
\end{poemblock}
