\begin{flushleft}
  \vspace*{\fill}
  Christmas has always invited me to look past the bustle of gifts and glitter and remember the moment that changed history: the birth of Jesus Christ.  I long for a celebration that turns our eyes back to that humble manger and the promise it carried—that God Himself stepped into our world to walk beside us.\\
\medskip
This past season I discovered the quiet art of bookbinding.  My first faltering stitches, pressed pages, and carefully glued spines reminded me that true gifts are fashioned by patient hands and a willing heart, not purchased from a shelf.  With every fold and thread in this little volume, I hoped to weave gratitude and love into something uniquely ours—something handmade rather than store-bought.\\
\medskip
Though my trust in God never vanished, grief once clouded it.  Losing loved ones left me angry and confused, and for many years my prayers were edged with resentment.  What finally eased that bitterness was returning to the story recorded in these pages: Jesus walked among us as a man.  He shared our hunger, fatigue, laughter, and sorrow—and, as a man, He chose to bear the cross for us.  That willing, human decision showed me that God does not stand apart from pain; He steps into it and redeems it.\\
\medskip
So this hand-bound copy of the New Testament is more than paper and ink.  It is a small testament to renewal—of craft, of Christmas, and of faith.  My prayer is that, as you read, you will feel the same quiet wonder that guided my hands: the assurance that Immanuel, “God with us,” still walks beside us today and invites us to do the same for one another.\\
  \bigskip
With Love, \\
  \medskip
--Arthur
  \vspace*{\fill}
\end{flushleft}
\newpage
